The pollination trade-off

### 2019-03-14 paper/manuscript.Rmd
Calculate R2 of models in the workflow

```{r model-fit-statistics}
drake::loadd(model_formula_ranking, glanced_fixed)

r2_values <- model_formula_ranking$by_model_set %>%
  dplyr::filter(grepl("abs", pollen_category)) %>% 
  dplyr::group_by(pollen_category) %>%
  dplyr::filter(delta_AIC_median == min(delta_AIC_median)) %>%
  dplyr::select(fixed_formula, pollen_category, scale) %>%
  dplyr::left_join(glanced_fixed) %>% 
  dplyr::select(r2m, r2c) %>%
  dplyr::summarise_all(dplyr::funs(min, median, mean, max)) %>%
  dplyr::mutate_if(is.numeric, round, digits = 2)
```

>>>>

```{r model-fit-statistics}
drake::loadd(r2_values)
```
